Chemical tagging: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-14 papers/clusters.tex
figure

@@

\section{Method and results}

Although only hints of small-scale clustering in the abundance space
are visible in \figurename~DWH, exploration of the data indicates that
known clusters do appear in the abundance space as over-densities.
This encourages us to look for over-densities automatically in the
abundance space and see if anything found that way would be over-dense
in phase space.
The simplest method for clustering points in $D$-dimensional space is
the \emph{k-means} algorithm (DWH CITE).
This algorithm is fast and performs well in practice in problems of
this nature.

>>>>

% figure shit
\newcommand{\insanefigure}[1]{%
\includegraphics[width=0.33\textwidth]{./figs/#1_MgFe.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_NaO.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_CN.png}\\
\includegraphics[width=0.33\textwidth]{./figs/#1_AlMg.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_SAl.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_MgK.png}\\
\includegraphics[width=0.33\textwidth]{./figs/#1_HR.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_sky.png}%
\includegraphics[width=0.33\textwidth]{./figs/#1_decv.png}}

@@

\begin{figure}[!p]
\insanefigure{all}
\caption{Whatevsinator.\label{fig:all}}
\end{figure}

\clearpage{}
\section{Method and results}

Although only hints of small-scale clustering in the abundance space
are visible in \figurename~\ref{fig:all}, exploration of the data indicates that
known clusters do appear in the abundance space as over-densities.
This encourages us to look for over-densities automatically in the
abundance space and see if anything found that way would be over-dense
in phase space.
The simplest method for clustering points in $D$-dimensional space is
the \emph{k-means} algorithm (DWH CITE).
This algorithm is fast and performs well in practice in problems of
this nature.
